Title here

### 2014-11-30 lnbip.tex
Updated abstract

\begin{abstract}        % give a summary of your paper
Delivering more value to the customer is the goal of every software company. In modern software business, delivering value in real-time requires a company to utilize real-time deployment of software, data-driven decisions and empirical evaluation of new products and features. These practices shorten the feedback loop and allow for faster reaction times, ensuring the development is focused on features providing real value. This thesis investigates practices known as continuous delivery and continuous experimentation as means of providing value for the customers in real-time. Continuous delivery is a development practice where the software functionality is deployed continuously to customer environment. This process includes automated builds, automated testing and automated deployment. Continuous experimentation is a development practice where the entire R\&D process is guided by conducting experiments and collecting feedback. As a part of this thesis, a case study is conducted in a medium-sized software company. The research objective is to analyze the challenges, benefits and organizational aspects of continuous delivery and continuous experimentation in the B2B domain. The data is collected from interviews conducted on members of two teams developing two different software products. The results suggest that technical challenges are only one part of the challenges a company encounters in this transition. For continuous delivery, the company must also address challenges related to the customer and procedures. The core challenges are caused by having multiple customers with diverse environments and unique properties, whose business depends on the software product. Some customers also require to perform manual acceptance testing, which slows down production deployments. For continuous experimentation, the company also has to address challenges related to the customer and organizational culture. An experiment which reveals value for a single customer might not reveal as much value for other customers due to unique properties in each customers business. Additionally, the speed by which experiments can be conducted is relative to the speed by which production deployments can be made. The benefits found from these practices support the case company in solving many of its business problems. The company can expose the software functionality to the customers from an earlier stage, and guide the product development by utilizing feedback and data instead of opinions.
%                         please supply keywords within your abstract
\keywords {Continuous delivery, Development process, B2B}
\end{abstract}
%
\section{Introduction}

\noindent \textbf{RQ1: What are the B2B specific challenges of continuous delivery and continuous experimentation?}

@@

%Interview results have to be compared to literature review results
\noindent \textbf{RQ2: How do continuous delivery and continuous experimentation benefit the case company?} %What are the problems and strengths of the current development process?

>>>>

\begin{abstract}        % give a summary of your paper
Delivering more value to the customer is the goal of every software company. In modern software business, delivering value in real-time requires a company to utilize real-time deployment of software to expose features to users faster, and to shorten the feedback loop. This allows for faster reaction times, ensuring the development is focused on features providing real value. This paper investigates practice known as continuous delivery andas means of providing value for the customers in real-time. Continuous delivery is a development practice where the software functionality is deployed continuously to customer environment. This process includes automated builds, automated testing and automated deployment. As a part of this paper, a case study is conducted in a medium-sized software company. The research objective is to analyze the challenges, benefits and organizational aspects of continuous delivery in the B2B domain. The data is collected from interviews conducted on members of two teams developing two different software products. The results suggest that technical challenges are only one part of the challenges a company encounters in this transition. For continuous delivery, the company must also address challenges related to the customer and procedures. The core challenges are caused by having multiple customers with diverse environments and unique properties, whose business depends on the software product. Some customers also require to perform manual acceptance testing, which slows down production deployments. The benefits found from continuous delivery support the case company in solving many of its business problems. The company can expose the software functionality to the customers from an earlier stage, and guide the product development by utilizing feedback and data instead of opinions.
%                         please supply keywords within your abstract
\keywords {Continuous delivery, Development process, B2B}
\end{abstract}
%
\section{Introduction}

To deliver value fast and to cope with the increasingly active business environment, companies have to find solutions that improve efficiency and speed. Agile practices \cite{cockburn2002agile} have increased the ability of software companies to cope with changing customer requirements and changing market needs \cite{dzamashvili2010impact}. To even further increase the efficiency, shortening the feedback cycle enables faster customer feedback.

Continuous delivery is a design practice aiming to shorten the delivery cycles and by automating the deployment process. It is an extension to continuous integration, where the software functionality is deployed frequently to customer environment, and the software is developed in a way that it is always ready for release. While continuous integration defines a process where the work is automatically built, tested and frequently integrated to mainline \cite{duvall2007continuous}, continuous delivery adds automated acceptance testing and automated deployment. Continuous delivery therefore attempts to deliver an idea to users as fast as possible.

This study is an exploratory deductive case study, which explores how continuous delivery be applied in the case company. While existing studies of applying the development models exist \cite{neely2013continuous}, none of the studies focuses specifically in the B2B domain. This study specifically aims to identify the main requirements, problems and key success factors with regards to continuous deliver in the B2B domain. Extending the development process towards continuous delivery requires a deep analysis of the current development and deployment process, seeking the current problems and strengths. Adopting continuous deliveryalso requires understanding the requirements of continuous delivery, and restrictions caused by the developed software products.

In this research, the units under the study are two teams and the two software products developed by these teams. By focusing on two different products, a broader view on the application and consequences of these development approaches can be gained. The first product, a marketing automation called Dialog, is used through an extensive user interface. The second product under inspection is CDM, a Master Data Management \cite{loshin2010master} solution running as an integrated background application. The objective of this thesis can therefore be summarized as follows:

\noindent \textbf{RQ1: What are the B2B specific challenges of continuous delivery?}

@@

%Interview results have to be compared to literature review results
\noindent \textbf{RQ2: How does continuous delivery benefit the case company?} %What are the problems and strengths of the current development process?
